Gaps in stellar streams as a result of globular cluster fly-bys

### 2024-12-19 paper/main.tex
typos

\section{Methods}
  The most accurate model of the Palomar~5 stream would involve full modeling of the internal dynamics of the cluster. This would mean computing $N$-Body interactions with a $\mathcal{O}(N^2)$ computation time, stellar evolution, super novae, an initial mass distirbution, treatment of binary star systems, etc. \citep[for such an example][see,]{2021NatAs...5..957G, 2016MNRAS.458.1450W}. Instead, We opt for solving the restricted-three body problem or particle-test method as we did for \citet{2023A&A...673A..44F}, which we present here for completeness.

>>>>

\section{Methods}
  The most accurate model of the Palomar~5 stream would involve full modeling of the internal dynamics of the cluster. This would mean computing $N$-Body interactions with a $\mathcal{O}(N^2)$ computation time, stellar evolution, super novae, an initial mass distirbution, treatment of binary star systems, etc. \citep[for such an example, see][]{2021NatAs...5..957G, 2016MNRAS.458.1450W}. Instead, we opt for solving the restricted-three body problem or particle-test method as we did for \citet{2023A&A...673A..44F}, which we present here for completeness.
